Stock enhancement undermines ecological stability

### 2022-02-23 rmd/manuscript.Rmd
edit: manuscript

---
title: "Stock enhancement undermines ecological stability"
output:
  word_document:
    reference_docx: word_format.docx
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
---

@@

The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals (stock enhancement). Still, we may underestimate the negative impact because current schemes rarely consider the consequences of stock enhancement for the whole ecological community. Here, we use theory and long-term data of Japanese stream fish communities to show that stock enhancement undermines community stability. Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion. Consistent with this prediction, fish communities showed greater temporal fluctuations and reduced biodiversity in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in the region. Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.

@@

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $Normal(0,\sigma_{\epsilon}^2)$. To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$). The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:

@@

We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Masato Yamamichi for helpful discussion on this manuscript. Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.

>>>>

---
title: "Stock enhancement undermines ecological stability"
output:
  pdf_document:
    latex_engine: xelatex
#  word_document:
#    reference_docx: word_format.docx
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
---

@@

The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals (stock enhancement). Still, we may underestimate the negative impact because current schemes rarely consider the consequences of stock enhancement for the whole ecological community. Here, we use theory and long-term data of Japanese stream fish communities to show that stock enhancement undermines community stability. Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion. Consistent with this prediction, fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in the region. Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.

@@

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $Normal(0,\sigma_{\epsilon}^2)$. To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0.5,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$). The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:

@@

We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Masato Yamamichi for helpful discussion on this manuscript. Data and codes will be made available upon the acceptance of the manuscript.
